---
title: "R Notebook"
author: "Thitima Moungsesai"
output:
  pdf_document: default
  html_notebook: default
---

# **Hello world!**
I'm learning R Markdown to create documents by using The Diamonds data set for exploration.


Format

=> data frame with 53940 rows and 10 variables:

=> Price : price in US dollars (\$326–\$18,823)

=> carat : weight of the diamond (0.2–5.01)

=> cut : quality of the cut (Fair, Good, Very Good, Premium, Ideal)

=> color : diamond colour, from D (best) to J (worst)

=> clarity : a measurement of how clear the diamond is (I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best))

=> x : length in mm (0–10.74)

=> y : width in mm (0–58.9)

=> z : depth in mm (0–31.8)

=> depth : total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43–79)

=> table : width of top of diamond relative to widest point (43–95)


```{r}
library(dplyr)
library('ggplot2')
print("Hello world")
head(diamonds)
```
## Diamonds exploration
## 1.Explore the number of cut.
```{r}
ggplot(diamonds,aes(cut,fill = cut))+geom_bar()
```

# 2.Explore by use bar graph for compare proportion the color of each cut.
```{r}
ggplot(diamonds,aes(cut,fill = color))+geom_bar(position = "fill")+
  theme_minimal()
```

# 3.Explore correlation by Scatter Plot : x is carat, y is price.
## Result :  positive correlation
```{r}
set.seed(42)
ggplot(sample_n(diamonds,1000),
      aes(carat,price))+
      geom_point(alpha=0.5)+
      geom_smooth(method = "lm")+
  labs(
    title = "Relationship between carat and price of diamonds ",
    x = "Carat",
    y = "Price (USD)",
    subtitle = "using ggplot to create this visualization",
    caption =  "Source : ggplot package" 
  )
```

# 4.Explore data and isolate graph by function : facet_wrap "Relationship between carat, price and cut of diamonds "
```{r}
set.seed(42)
ggplot(sample_n(diamonds,7000),
      aes(carat,price,color=cut))+
      geom_point(alpha=0.5)+
      geom_smooth(method = "lm")+
  labs(
    title = "Relationship between carat, price and cut of diamonds ",
    x = "Carat",
    y = "Price (USD)",
    subtitle = "using ggplot to create this visualization",
    caption =  "Source : ggplot package" 
  )+
  facet_wrap(~cut,ncol=5)
```

# 5.Explore data and isolate graph by function : facet_grid "Relationship between carat, price and cut of diamonds "

```{r}
set.seed(25)
diamonds %>%
  sample_n(10000) %>%
  ggplot( aes(carat, price)) +
  geom_point(alpha=0.4) +
  geom_smooth() +
  theme_minimal() +
  facet_grid(cut ~ color)   #cross between : x=cut, y=color
```
