---
title: "R Notebook"
author: "Thitima Moungsesai"
output:
  pdf_document: default
  html_notebook: default
  word_document: default
---
# **Hello world!**
I'm learning R Markdown to create documents by using The mtcars data set for exploration.


Format

A data frame with 32 observations on 11 (numeric) variables.


=> mpg	Miles/(US) gallon

=> cyl	Number of cylinders

=> disp	Displacement (cu.in.)

=> hp	Gross horsepower

=> drat	Rear axle ratio

=> wt	Weight (1000 lbs)

=> qsec	1/4 mile time

=> vs	Engine (0 = V-shaped, 1 = straight)

=> am	Transmission (0 = automatic, 1 = manual)

=> gear	Number of forward gears

=> carb	Number of carburetors


```{r}
library(dplyr)
library(ggplot2)
print("Hello word")
head(mtcars)
```

# 1.Simple histogram

```{r}
ggplot(mtcars, 
       aes(mpg)) +
  geom_histogram(bins=10)
```




# 2.Simple boxplot

```{r}
ggplot(mtcars,aes(mpg))+
  geom_boxplot()
```

# EDA => Exploratory Data Analysis

# 3.Find the number of Auto and Manual.

```{r}
m <- mtcars %>%
  tibble() %>%
  mutate(am = factor(if_else(am==0, "Auto", "Manual")))

glimpse(m)
```
```{r}
m %>% 
  count(am)%>%
  mutate(pct = n/sum(n))

ggplot(m,aes(am))+
  geom_bar()
```

# 4.Find correlation of the weight vs miles per gallon by The scatterplot has a linear model.
## Result : negative correlation when As the weight increases, the MPG decreases. 

```{r}
ggplot(m, aes(wt, mpg)) +
  geom_point(color = "salmon",
             size = 1,
             alpha = 0.8) +
  geom_smooth(method = "lm",
              color = "black",
              fill = "blue")+
  labs(
    title = "Relationship between weight vs miles per gallon",
    x = "wt (weight)",
    y = "mpg(miles per gallon)")
```

# 5.The scatterplot of the weight vs miles per gallon and represent data point following "vs" column.

```{r}
ggplot(m,aes(wt,mpg))+
  geom_point(size = 6,
             alpha = 0.5,
             mapping = aes(color = factor(vs)))+
  labs(
    title = "Relationship between weight vs miles per gallon",
    x = "wt (weight)",
    y = "mpg(miles per gallon)")
```

# 6.The scatterplot of the weight vs miles per gallon and represent data point following "hp_segment" column.

```{r}
m %>%
  select(wt, mpg, hp) %>%
  mutate(hp_segment = case_when( 
    hp < 100 ~ "low",
    hp < 200 ~ "medium",
    TRUE ~ "high"
  )) %>% 
  mutate(hp_segment = factor(   
      hp_segment,
      labels = c("low", "medium", "high"),   
      levels = c("low", "medium", "high"),   
      ordered = TRUE) ) %>%   
  ggplot(   mapping = aes(wt, mpg, 
                       color=hp_segment)) +
    geom_point(size=4, alpha=0.8) +
    scale_color_manual(values = c("red",      
                                  "gold",     
                                  "blue"))+
  labs(
    title = "Relationship between weight vs miles per gallon",
    x = "wt (weight)",
    y = "mpg(miles per gallon)")
```

# 7.Combind Chart

```{r}
library(ggplot2)
library(patchwork)
p1 <- ggplot(mtcars, aes(hp)) + geom_histogram(bins=10)
p2 <- ggplot(mtcars, aes(mpg)) + geom_density()
p3 <- ggplot(diamonds, aes(cut, fill=cut)) + geom_bar()



( p1 + p2 ) / p3 
```

