---
title: "R Notebook"
author: "Thitima Moungsesai"
output:
  pdf_document: default
  html_notebook: default
  word_document: default
---
# **Hello world!**
I'm learning R Markdown to create documents by using The flights data set for exploration.

=> year, month, day : Date of departure.

=>dep_time, arr_time : Actual departure and arrival times (format HHMM or HMM), local tz.

=> sched_dep_time, sched_arr_time : Scheduled departure and arrival times (format HHMM or HMM), local tz.

=> dep_delay, arr_delay : Departure and arrival delays, in minutes. Negative times represent early departures/arrivals.

=> carrier: Two letter carrier abbreviation. See airlines to get name.

=> flight : Flight number.

=> tailnum : Plane tail number. See planes for additional metadata.

=> origin, dest : Origin and destination. See airports for additional metadata.

=> air_time : Amount of time spent in the air, in minutes.

=> distance : Distance between airports, in miles.

=> hour, minute : Time of scheduled departure broken into hour and minutes.

=> time_hour : Scheduled date and hour of the flight as a POSIXct date. Along with origin, can be used to join flights data to weather data.

```{r}
#install.packages("knitr")
library(knitr)
#install.packages("tinytex")
#tinytex::install_tinytex()

library(dplyr)
library(nycflights13)
library(ggplot2)

#View(flights)
```
# 1.How many flight of each month?
```{r}

flights%>%
  count(month)%>%
  arrange(desc(n))

ggplot(flights,aes(factor(month)))+
  geom_bar()+
  labs(title = "month vs total flights of each month",
    x = "month",
    y = "total flights of each month",
    subtitle = "using ggplot to create this visualization",
    caption =  "Source : ggplot package" )
```

# 2.Explore data by use bar graph for compare proportion the month of each carrier.

```{r}
ggplot(flights,aes(factor(month),fill=carrier))+
geom_bar(position = "fill")+
  labs(title = "month vs total flights of each month",
    x = "month",
    y = "total flights of each month",
    subtitle = "using ggplot to create this visualization",
    caption =  "Source : ggplot package" )
```

# 3.Which carrier had most flights in May 2013?
## Result : the carrier had the most flights is UA
```{r}
flights%>%
  filter(month == 5,year == 2013)%>%
  count(carrier)%>%
  arrange(desc(n))

flights%>%
  filter(month == 5,year == 2013)%>%
  ggplot(aes(carrier,fill=carrier))+
  geom_bar()+
  labs(title = "carrier vs total flights in May 2013",
    x = "carrier",
    y = "total flights",
    subtitle = "using ggplot to create this visualization",
    caption =  "Source : ggplot package" 
  )

```

# 4.Where is the Top 10 of destination that people are popular to go?
## Result : ORD >> ATL >> LAX >> BOS >> MCO >> CLT >> SFO >> FLL >> MIA >> DCA 

```{r}
A <-flights%>%
  count(dest)%>%
  arrange(desc(n))%>%
  head(10)
A
  ggplot(A,aes(dest,n))+
    geom_col(position = "stack")+
    geom_text(aes(label=n), vjust=-0.25)+
    labs(title = "Destination vs flights ",
    x = "Destination",
    y = "flights",
    subtitle = "using ggplot to create this visualization",
    caption =  "Source : ggplot package" )
```

# 5.Which carrier has the most airtime?
## Result : The carrier has most airtime is UA

```{r}
flights %>%
    filter(!is.na(air_time))%>%
    group_by(carrier)%>%
    summarise(total_air_time_Hrs = round(sum(air_time)/60,2))


flights %>%
    filter(!is.na(air_time))%>%
    group_by(carrier)%>%
    summarise(total_air_time_Hrs = round(sum(air_time)/60,2))%>%
    arrange(desc(total_air_time_Hrs)) %>%
ggplot(aes(carrier,total_air_time_Hrs))+
geom_col(position = "stack")+
  labs(title = "Carrier vs total_air_time_Hrs ",
    x = "Carrier",
    y = "total_air_time_Hrs",
    subtitle = "using ggplot to create this visualization",
    caption =  "Source : ggplot package" )
```

# 6.Find the trends of flights for each carrier in 2013
## Result : Almost the trend of flight for carrier to be stable except "OO","MQ",Which have decreased.
```{r}
ggplot(flights,
      aes(month,flight,color=carrier))+
      geom_smooth(method = "lm")+
  labs(
    title = "Relationship month, flight of carrier ",
    x = "month",
    y = "flight",
    subtitle = "using ggplot to create this visualization",
    caption =  "Source : ggplot package" )+
    facet_wrap(~carrier,ncol=5)
```





