---
title: "R Notebook"
author: "Thitima Moungsesai"
output: pdf_document
---

# **Hello world!**
I'm learning R Markdown to create documents by using The titanic_train data set for logistic regression to predict binary outcome (0,1)

Format
Data frame with columns

=> PassengerId : Passenger ID

=> Survived : Passenger Survival Indicator

=> Pclass : Passenger Class

=> Name : Name

=> Sex : Sex

=> Age : Age

=> SibSp : Number of Siblings/Spouses Aboard

=> Parch : Number of Parents/Children Aboard

=> Ticket : Ticket Number

=> Fare : Passenger Fare

=> Cabin : Cabin

=> Embarke : Port of Embarkation

```{r}
#install.packages("titanic")
library(titanic)
library(dplyr)

?titanic_train

```
# Drop NA (Missing Value)
```{r}
titanic_train <- na.omit(titanic_train)
nrow(titanic_train)
glimpse(titanic_train)

```
# Split data
```{r}
set.seed(42)
n<- nrow(titanic_train)
id<- sample(1:n,size = n*0.7) ##70% train 30% test
train_data <- titanic_train[id, ]
nrow(train_data)
test_data<-titanic_train[-id, ]
nrow(test_data)
```
# **Train data**
```{r}
## Train Model
model_train <- glm(Survived ~ Pclass + Age ,data = train_data,family = "binomial")
summary(model_train)
```

```{r}
## Predict and Evaluate model
train_data$prob_survived <- predict(model_train,type = "response")
train_data$preb_survived <- ifelse(train_data$prob_survived >=0.5,1,0)
```

```{r}
## Confusion matrix of Train Model
conM_train <- table(train_data$Survived,train_data$preb_survived,dnn = c("Predicted","Actual"))
conM_train

acc_train <- (conM_train[1,1] + conM_train[2,2])/sum(conM_train)
prec_train <- conM_train[2,2] / (conM_train[1,2] + conM_train[2,2])
rec_train <- conM_train[2,2]/(conM_train[2,1]+conM_train[2,2])
f1_train <- 2*(( prec_train* rec_train)/(prec_train + rec_train))

cat("Train Model :","\n--------------------","\nAccuracy",acc_train,"\nprecision",prec_train,"\nRecall",rec_train,"\nF1 score",f1_train)
```
# **Test data**
```{r}
## Test Model
model_test <- glm(Survived ~ Pclass + Age ,data = test_data,family = "binomial")
summary(model_test)
```

```{r}
## Predict and Evaluate model
test_data$prob_survived <- predict(model_test,type = "response")
test_data$preb_survived <- ifelse(test_data$prob_survived >=0.5,1,0)
```

```{r}
## Confusion matrix of Test Model
conM_test <- table(test_data$Survived,test_data$preb_survived,dnn = c("Predicted","Actual"))
conM_test

acc_test <- (conM_test[1,1] + conM_test[2,2])/sum(conM_test)
prec_test <- conM_test[2,2] / (conM_test[1,2] + conM_test[2,2])
rec_test <- conM_test[2,2]/(conM_test[2,1]+conM_test[2,2])
f1_test <- 2*(( prec_test* rec_test)/(prec_test + rec_test))

cat("\nTest Model :","\n--------------------","\nAccuracy",acc_test,"\nprecision",prec_test,"\nRecall",rec_test,"\nF1 score",f1_test)
```















